---
title: "lme_mods"
author: "Jacob Salminen"
date: "2024-04-19"
output:
  html_document:
    df_print: paged
  pdf_document: default
---

```{r setup, include=FALSE}
# ERROR. png() device not found bug try: dev.off()
# ERROR. png() device not found fixed by changing cell names to a simple "windows friendlY" format so that knitr could save files.
knitr::opts_chunk$set(echo = TRUE)
```

# Packages & Setup
```{r}
# install.packages(c("tidyverse","purrr","R.matlab","readxl","dplyr"))
library(readxl);
library(purrr)
library(tidyverse);
library(tibble);
library(knitr);
library(gtsummary);
library(kableExtra);
library(lme4);
library(MuMIn);
```

## GTSUMMARY THEME
``` {r}
# my_theme <-
#   list(
#     "tbl_summary-str:default_con_type" = "continuous2",
#     "tbl_summary-str:continuous_stat" = c(
#       "{median} ({p25} - {p75})",
#       "{mean} ({sd})",
#       "{min} - {max}"
#     ),
#     "tbl_summary-str:categorical_stat" = "{n} / {N} ({p}%)",
#     "style_number-arg:big.mark" = "",
#     "tbl_summary-fn:percent_fun" = function(x) style_percent(x, digits = 3)
#   )
# my_theme <-
#   list()
# gtsummary::set_gtsummary_theme(my_theme)
gtsummary::set_gtsummary_theme(theme_gtsummary_journal("jama"))
# reset_gtsummary_theme()
```

## load table 
```{r} 
# excel_dir <-"M:/jsalminen/GitHub/par_EEGProcessing/src/_data/MIM_dataset/_studies/04162024_MIM_YAOAN89_antsnormalize_iccREMG0p4_powpow0p3_skull0p01/cluster/icrej_5/12/spec_data/group_spec/psd_calcs/fooof_kinematics_table.xlsx";
excel_dir <-"M:/jsalminen/GitHub/par_EEGProcessing/src/_data/MIM_dataset/_studies/04232024_MIM_YAOAN89_antsnorm_dipfix_iccREMG0p4_powpow0p3_skull0p01_15mmrej/cluster/icrej_5/11/spec_data/group_spec/psd_calcs/fooof_kinematics_table_nans.xlsx";
eegt <- read_excel(excel_dir,sheet="Sheet1") 
```

## get unique entries 
```{r} 

#%% KIN PARAMS
kin_measures = c('mean_APexc_COV','mean_APexc_mean','mean_MLexc_COV','mean_MLexc_mean','mean_StepDur','mean_StepDur_cov','mean_UDexc_COV','mean_UDexc_mean','mean_StanceDur','mean_GaitCycleDur','mean_PeakUpDownVel_mean');
kin_title_chars = c("AP Exc. COV","AP Exc. Mean","ML Exc. COV","ML Exc. Mean","Step Dur.","Step Dur. COV","UD Exc. COV","UD Exc Mean","Stance Dur.","Gait Cycle Dur.","Peak UD Vel. Mean")
# kin_inds_plot = c(1:length(kin_measures));
kin_inds_plot = c(1,3,6,5,7);
#%% EEG PARAMS
clusters = unique(eegt$cluster_id);
subjects = unique(eegt$subj_char);
groups = unique(eegt$group_char);
# eeg_measures = c('theta_avg_power','alpha_avg_power','beta_avg_power','beta_div_theta','theta_div_beta','log_beta_div_theta','log_theta_div_beta','aperiodic_exp','aperiodic_offset');
# eeg_title_chars = c("**THETA**","**ALPHA**","**BETA**","**BETA/THETA**","**THETA/BETA**","**log10(BETA/THETA)**","**log10(THETA/BETA)**","**AP exp**","**AP offset**");
eeg_measures = c('theta_avg_power','alpha_avg_power','beta_avg_power','theta_div_beta','log_theta_div_beta','aperiodic_exp','aperiodic_offset');
eeg_title_chars = c("**THETA**","**ALPHA**","**BETA**","**THETA/BETA**","**log10(THETA/BETA)**","**AP exp**","**AP offset**");
# eeg_inds_plot = c(1:length(eeg_title_chars));
eeg_inds_plot = c(1,2,3,4);
cluster_inds_plot = c(10,5,2,6,9);
```

## get speeds only 
```{r} 
eegt <- filter_at(eegt,vars('cond_char'), any_vars(. %in% c('0.25','0.5','0.75','1.0')))
flat_speeds = unique(eegt$cond_char)
eegt$cond_char <- as.numeric(eegt$cond_char)
eegt$speed_cond_num <- as.numeric(eegt$cond_char)
eegt <- mutate(eegt,across(c('subj_char'), factor))
eegt <- mutate(eegt,across(c('group_char'), factor))
eegt$speed_ord <- cut(eegt$cond_char, 4, ordered = TRUE)
eegt <- mutate(eegt,across(c('cond_char'), factor))
eegt$group_speed_code = paste(eegt$group_char,eegt$cond_char,sep="_")
head(eegt)
```


## create ratios 
```{r conversions}
Log <- function(x, base = exp(1)) {
  LOG <- base::log(as.complex(x), base = base)
  if (all(Im(LOG) == 0)) { LOG <- Re(LOG) }
  LOG }
#%% CALCS
eegt <- eegt%>%
  mutate(beta_div_theta=beta_avg_power/theta_avg_power)
eegt <- eegt%>%
  mutate(theta_div_beta=theta_avg_power/beta_avg_power)
# eegt <- eegt%>%
#   mutate(log_beta_div_theta=log10(beta_avg_power/theta_avg_power+max(abs(beta_avg_power/theta_avg_power))))
# eegt <- eegt%>%
#   mutate(log_theta_div_beta=log10(theta_avg_power/beta_avg_power+max(abs(theta_avg_power/beta_avg_power))))
# eegt <- eegt%>%
#   mutate(log_beta_div_theta=log10(beta_avg_power/theta_avg_power+mean(abs(beta_avg_power/theta_avg_power))/(mean(abs(beta_avg_power/theta_avg_power))+3*sd(abs(beta_avg_power/theta_avg_power)))));
# eegt <- eegt%>%
#   mutate(log_theta_div_beta=log10(theta_avg_power/beta_avg_power+mean(abs(theta_avg_power/beta_avg_power))/(mean(abs(theta_avg_power/beta_avg_power))+3*sd(abs(theta_avg_power/beta_avg_power)))));
# eegt <- eegt%>%
#   mutate(log_beta_div_theta=log10((beta_avg_power/theta_avg_power)+abs(min((beta_avg_power/theta_avg_power)))));
# eegt <- eegt%>%
#   mutate(log_theta_div_beta=log10((theta_avg_power/beta_avg_power)+abs(min((theta_avg_power/beta_avg_power)))));
# eegt <- eegt%>%
#   mutate(log_beta_div_theta=Re(Log((beta_avg_power/theta_avg_power),10)*Conj(Log((theta_avg_power/beta_avg_power),10))));
# eegt <- eegt%>%
#   mutate(log_theta_div_beta=Re(Log((theta_avg_power/beta_avg_power),10)*Conj(Log((theta_avg_power/beta_avg_power),10))));
eegt <- eegt%>%
  mutate(log_beta_div_theta=Re(Log((beta_avg_power/theta_avg_power),10)));
eegt <- eegt%>%
  mutate(log_theta_div_beta=Re(Log((theta_avg_power/beta_avg_power),10)));
```
# EEG TESTS: SPEED, GROUP, INTERACTION
## LME EEG ~ 1+speed+group+speed:group
```{r eegspeedgroupinter, echo=FALSE, message=FALSE, results="asis"}
library(gtsummary)
# inter_pvalue = vector(mode="logical");
for (ci in cluster_inds_plot) {
  tmpt <- filter_at(eegt,vars('cluster_id'), any_vars(. %in% clusters[ci]));
  for(ki in kin_inds_plot){
    tmpt = tmpt[complete.cases(tmpt[[kin_measures[ki]]]),]
  }
  tbl <- tibble(outcome=eeg_measures[eeg_inds_plot]) %>%
    rowwise() %>%
    mutate(
      tbl = 
        lmer(str_glue("{outcome} ~ 1 + speed_cond_num + group_char + speed_cond_num:group_char + (1|subj_char)"), data=tmpt) %>%
        tbl_regression(tidy_fun = broom.mixed::tidy,
                       pvalue_fun = purrr::partial(style_pvalue, digits = 2),
                       intercept=TRUE) %>%
        add_global_p() %>%
        add_q() %>%
        list()
      ) %>%
    pull(tbl) %>%
    tbl_merge(tab_spanner=eeg_title_chars[eeg_inds_plot])
  
  t_out <- as_gt(tbl) %>%
    gt::tab_header(title=c("Cluster: ",clusters[ci])) %>%
    gt::as_raw_html()
  print(t_out)
  
  rsq <- tibble(outcome=eeg_measures[eeg_inds_plot]) %>%
    rowwise() %>%
    mutate(
        mod = 
          lmer(str_glue("{outcome} ~ 1 + speed_cond_num + group_char + speed_cond_num:group_char + (1|subj_char)"), data=tmpt) %>%
          r.squaredGLMM(),
          print(str_glue("{outcome}\n R2m: {round(mod[1],4)},\tR2c: {round(mod[2],4)}\n\n"))
    )
  
  #%% VISUALIZATION OF MODELS
  theme_set(theme_classic()) # This sets the default ggplot theme
  fitfit <- tibble(outcome=eeg_measures[eeg_inds_plot]) %>%
    rowwise() %>%
    mutate(
        mod = 
          lmer(str_glue("{outcome} ~ 1 + speed_cond_num + group_char + speed_cond_num:group_char + (1|subj_char)"), data=tmpt)%>%
          list()
    )
  for(modi in 1:length(eeg_measures[eeg_inds_plot])){
    eegi = eeg_inds_plot[modi]
    tmpt <- tmpt %>%
      mutate(fit.m = predict(fitfit$mod[[modi]], re.form = NA),
             fit.c = predict(fitfit$mod[[modi]], re.form = NULL))
    print(
      tmpt %>%
        ggplot(aes(x = speed_cond_num, y = .data[[eeg_measures[eegi]]], group = subj_char, col=group_char)) +
        geom_point(pch=16, size=2, alpha=0.5) +
        geom_line(aes(x= speed_cond_num, y=fit.c, group = subj_char),color="grey", size = .1) +
        geom_line(aes(x= speed_cond_num, y=fit.m, col = group_char), size = 2)+
        facet_wrap(vars(group_char))+
        ggtitle(eeg_measures[eegi])+ 
        guides(group="none")
    )
  }
  
  # t_out <- as_gt(tbl) %>%
  #   gt::tab_header(title=c("Cluster: ",clusters[ci])) %>%
  #   gt::tab_options(table.layout = "fixed") %>%
  #   gt::as_raw_html()
  # print(t_out)
  
  # t_out <- as_kable_extra(tbl, format = "latex") %>%
  #   add_header_above(c("Cluster: ",clusters[ci])) %>%
  #   kable_styling(latex_options="scale_down")
  # 
  # cat(knitr::knit_print(t_out));
  # if (ci%%2 == 0){
  #   cat('\\clearpage');
  # }
}
```
## LME EEG ~ 1+speed+group
```{r eegspeedgroup, echo=FALSE, message=FALSE, results="asis"}
library(gtsummary)
inter_pvalue = vector(mode="logical");
for (ci in cluster_inds_plot) {
  tmpt <- filter_at(eegt,vars('cluster_id'), any_vars(. %in% clusters[ci]));
  for(ki in kin_inds_plot){
    tmpt = tmpt[complete.cases(tmpt[[kin_measures[ki]]]),]
  }
  tbl <- tibble(outcome=eeg_measures[eeg_inds_plot]) %>%
    rowwise() %>%
    mutate(
      tbl = 
        lmer(str_glue("{outcome} ~ 1 + speed_cond_num + group_char + (1|subj_char)"), data=tmpt) %>%
        tbl_regression(tidy_fun = broom.mixed::tidy,
                       pvalue_fun = purrr::partial(style_pvalue, digits = 2),
                       intercept=TRUE) %>%
        add_global_p() %>%
        add_q() %>%
        list()
      ) %>%
    pull(tbl) %>%
    tbl_merge(tab_spanner=eeg_title_chars[eeg_inds_plot])
  
  #%% PRINT HTML
  t_out <- as_gt(tbl) %>%
    gt::tab_header(title=c("Cluster: ",clusters[ci])) %>%
    gt::as_raw_html()
  print(t_out)
  
  rsq <- tibble(outcome=eeg_measures[eeg_inds_plot]) %>%
    rowwise() %>%
    mutate(
        mod = 
          lmer(str_glue("{outcome} ~ 1 + speed_cond_num + group_char + (1|subj_char)"), data=tmpt) %>%
          r.squaredGLMM(),
          print(str_glue("{outcome}\n R2m: {round(mod[1],4)},\tR2c: {round(mod[2],4)}\n\n"))
    )
  
  #%% VISUALIZATION OF MODELS
  theme_set(theme_classic()) # This sets the default ggplot theme
  fitfit <- tibble(outcome=eeg_measures[eeg_inds_plot]) %>%
    rowwise() %>%
    mutate(
        mod = 
          lmer(str_glue("{outcome} ~ 1 + speed_cond_num + group_char + (1|subj_char)"), data=tmpt)%>%
          list()
    )
  for(modi in 1:length(eeg_measures[eeg_inds_plot])){
    eegi = eeg_inds_plot[modi]
    tmpt <- tmpt %>%
      mutate(fit.m = predict(fitfit$mod[[modi]], re.form = NA),
             fit.c = predict(fitfit$mod[[modi]], re.form = NULL))
    print(
      tmpt %>%
        ggplot(aes(x = speed_cond_num, y = .data[[eeg_measures[eegi]]], group = subj_char, col=group_char)) +
        geom_point(pch=16, size=2, alpha=0.5) +
        geom_line(aes(x= speed_cond_num, y=fit.c, group = subj_char),color="grey", size = .1) +
        geom_line(aes(x= speed_cond_num, y=fit.m, col = group_char), size = 2)+
        facet_wrap(vars(group_char))+
        ggtitle(eeg_measures[eegi])+ 
        guides(group="none")
    )
  }
  
  #%% PRINT LATEX
  # t_out <- as_kable_extra(tbl, format = "latex") %>%
  #   add_header_above(c("Cluster: ",clusters[ci])) %>%
  #   kable_styling(latex_options="scale_down")
  # cat(knitr::knit_print(t_out));
  # if (ci%%2 == 0){
  #   cat('\\clearpage');
  # }
}
```
# KINEMATIC TESTS: SPEED, GROUP, INTERACTION
## LME KIN ~ 1+speed+group+speed:group
```{r kinspeedgroupinter, echo=FALSE, message=FALSE, results="asis"}
library(gtsummary)
for (ci in cluster_inds_plot) {
  tmpt <- filter_at(eegt,vars('cluster_id'), any_vars(. %in% clusters[ci]));
  for(ki in kin_inds_plot){
    tmpt = tmpt[complete.cases(tmpt[[kin_measures[ki]]]),]
  }
  tbl <- tibble(outcome=kin_measures[kin_inds_plot]) %>%
    rowwise() %>%
    mutate(
      tbl = 
        lmer(str_glue("{outcome} ~ 1 + speed_cond_num + group_char + speed_cond_num:group_char + (1|subj_char)"), data=tmpt) %>%
        tbl_regression(tidy_fun = broom.mixed::tidy,
                       pvalue_fun = purrr::partial(style_pvalue, digits = 2),
                       intercept=TRUE) %>%
        add_global_p() %>%
        add_q() %>%
        list()
      ) %>%
    pull(tbl) %>%
    tbl_merge(tab_spanner=kin_title_chars[kin_inds_plot])
  
  #%% PRINT HTML
  t_out <- as_gt(tbl) %>%
    gt::tab_header(title=c("Cluster: ",clusters[ci])) %>%
    gt::as_raw_html()
  print(t_out)
  
  rsq <- tibble(outcome=kin_measures[kin_inds_plot]) %>%
    rowwise() %>%
    mutate(
        mod = 
          lmer(str_glue("{outcome} ~ 1 + speed_cond_num + group_char + speed_cond_num:group_char + (1|subj_char)"), data=tmpt) %>%
          r.squaredGLMM(),
          print(str_glue("{outcome}\n R2m: {round(mod[1],4)},\tR2c: {round(mod[2],4)}\n\n"))
    )
  
  #%% VISUALIZATION OF MODELS
  theme_set(theme_classic()) # This sets the default ggplot theme
  fitfit <- tibble(outcome=kin_measures[kin_inds_plot]) %>%
    rowwise() %>%
    mutate(
        mod = 
          lmer(str_glue("{outcome} ~ 1 + speed_cond_num + group_char + speed_cond_num:group_char + (1|subj_char)"), data=tmpt)%>%
          list()
    )
  for(modi in 1:length(kin_measures[kin_inds_plot])){
    kini = kin_inds_plot[modi]
    tmpt <- tmpt %>%
      mutate(fit.m = predict(fitfit$mod[[modi]], re.form = NA),
             fit.c = predict(fitfit$mod[[modi]], re.form = NULL))
    print(
      tmpt %>%
        ggplot(aes(x = speed_cond_num, y = .data[[kin_measures[kini]]], group = subj_char, col=group_char)) +
        geom_point(pch=16, size=2, alpha=0.5) +
        geom_line(aes(x= speed_cond_num, y=fit.c, group = subj_char),color="grey", size = .1) +
        geom_line(aes(x= speed_cond_num, y=fit.m, col = group_char), size = 2)+
        facet_wrap(vars(group_char))+
        ggtitle(kin_measures[kini])+ 
        guides(group="none")
    )
  }
  
  # library(lme4)
  # library(MuMIn)
  # library(insight)
  # tmpt <- filter_at(eegt,vars('cluster_id'), any_vars(. %in% clusters[ci]));
  # mod = lmer(str_glue("{kin_measures[1]}~1 + speed_cond_num + group_char + speed_cond_num:group_char + (1|subj_char)"),data=tmpt)
  # Vf = var(predict(mod,re.form=NA))
  # Vr = get_variance(mod)$var.random
  # Ve = sigma(mod)^2
  # rglmm = r.squaredGLMM(mod)
  # R2m = Vf / (Vf + Vr + Ve)
  # R2c = (Vf + Vr) / (Vf + Vr + Ve)
  # print(rglmm); print(c(R2m,R2c))
  
  #%% PRINT LATEX
  # t_out <- as_kable_extra(tbl, format = "latex") %>%
  #   add_header_above(c("Cluster: ",clusters[ci])) %>%
  #   kable_styling(latex_options="scale_down")
  # cat(knitr::knit_print(t_out));
  # if (ci%%2 == 0){
  #   cat('\\clearpage');
  # }
}
```
## LME KIN ~ 1+speed+group
```{r kinspeedgroup, echo=FALSE, message=FALSE, results="asis"}
library(gtsummary)
for (ci in cluster_inds_plot) {
  tmpt <- filter_at(eegt,vars('cluster_id'), any_vars(. %in% clusters[ci]));
  for(ki in kin_inds_plot){
    tmpt = tmpt[complete.cases(tmpt[[kin_measures[ki]]]),]
  }
  tbl <- tibble(outcome=kin_measures[kin_inds_plot]) %>%
    rowwise() %>%
    mutate(
      tbl = 
        lmer(str_glue("{outcome} ~ 1 + speed_cond_num + group_char + (1|subj_char)"), data=tmpt) %>%
        tbl_regression(tidy_fun = broom.mixed::tidy,
                       pvalue_fun = purrr::partial(style_pvalue, digits = 2),
                       intercept=TRUE) %>%
        add_global_p() %>%
        add_q() %>%
        list()
      ) %>%
    pull(tbl) %>%
    tbl_merge(tab_spanner=kin_title_chars[kin_inds_plot])
  
  t_out <- as_gt(tbl) %>%
    gt::tab_header(title=c("Cluster: ",clusters[ci])) %>%
    gt::tab_options(table.layout = "fixed") %>%
    gt::as_raw_html()
  print(t_out)
  
  rsq <- tibble(outcome=kin_measures[kin_inds_plot]) %>%
    rowwise() %>%
    mutate(
        mod = 
          lmer(str_glue("{outcome} ~ 1 + speed_cond_num + group_char + (1|subj_char)"), data=tmpt) %>%
          r.squaredGLMM(),
          print(str_glue("{outcome}\n R2m: {round(mod[1],4)},\tR2c: {round(mod[2],4)}\n\n"))
    )
  
  #%% VISUALIZATION OF MODELS
  theme_set(theme_classic()) # This sets the default ggplot theme
  fitfit <- tibble(outcome=kin_measures[kin_inds_plot]) %>%
    rowwise() %>%
    mutate(
        mod = 
          lmer(str_glue("{outcome} ~ 1 + speed_cond_num + group_char + (1|subj_char)"), data=tmpt)%>%
          list()
    )
  for(modi in 1:length(kin_measures[kin_inds_plot])){
    kini = kin_inds_plot[modi]
    tmpt <- tmpt %>%
      mutate(fit.m = predict(fitfit$mod[[modi]], re.form = NA),
             fit.c = predict(fitfit$mod[[modi]], re.form = NULL))
    print(
      tmpt %>%
        ggplot(aes(x = speed_cond_num, y = .data[[kin_measures[kini]]], group = subj_char, col=group_char)) +
        geom_point(pch=16, size=2, alpha=0.5) +
        geom_line(aes(x= speed_cond_num, y=fit.c, group = subj_char),color="grey", size = .1) +
        geom_line(aes(x= speed_cond_num, y=fit.m, col = group_char), size = 2)+
        facet_wrap(vars(group_char))+
        ggtitle(kin_measures[kini])+ 
        guides(group="none")
    )
  }
  
  # t_out <- as_kable_extra(tbl, format = "latex") %>%
  #   add_header_above(c("Cluster: ",clusters[ci])) %>%
  #   kable_styling(latex_options="scale_down")
  # cat(knitr::knit_print(t_out));
  # if (ci%%2 == 0){
  #   cat('\\clearpage');
  # }
}
```
# EEG TESTS: KINEMATIC, GROUP, INTERACTION
## LME EEG ~ 1+kin+group+kin:group
```{r eegkingroupinter, echo=FALSE, message=FALSE, results="asis"}
library(gtsummary)
for (ci in cluster_inds_plot) {
  tmpt <- filter_at(eegt,vars('cluster_id'), any_vars(. %in% clusters[ci]));
  for(ki in kin_inds_plot){
    tmpt = tmpt[complete.cases(tmpt[[kin_measures[ki]]]),]
  }
  for (mi in 1:length(kin_measures)) {
    tbl <- tibble(outcome=eeg_measures[eeg_inds_plot]) %>%
      rowwise() %>%
      mutate(
        tbl = 
          lmer(str_glue(paste("{outcome} ~ 1 + ",kin_measures[mi]," + group_char + ",kin_measures[mi],":group_char + (1|subj_char)")), data=tmpt) %>%
          tbl_regression(tidy_fun = broom.mixed::tidy,
                         pvalue_fun = purrr::partial(style_pvalue, digits = 2),
                         intercept=TRUE) %>%
          add_global_p() %>%
          add_q() %>%
          list()
        ) %>%
      pull(tbl) %>% 
      tbl_merge(tab_spanner=eeg_title_chars[eeg_inds_plot])
    
    t_out <- as_gt(tbl) %>%
      gt::tab_header(title=c("Changes in ",kin_measures[ki],"for Cluster: ",clusters[ci])) %>%
      gt::tab_options(table.layout = "fixed") %>%
      gt::as_raw_html()
    print(t_out)
    
    rsq <- tibble(outcome=eeg_measures[eeg_inds_plot]) %>%
    rowwise() %>%
    mutate(
        mod = 
          lmer(str_glue(paste("{outcome} ~ 1 + ",kin_measures[mi]," + group_char + ",kin_measures[mi],":group_char + (1|subj_char)")), data=tmpt) %>%
          r.squaredGLMM(),
          print(str_glue("{outcome}\n R2m: {round(mod[1],4)},\tR2c: {round(mod[2],4)}\n\n"))
    )
    
    #%% VISUALIZATION OF MODELS
    theme_set(theme_classic()) # This sets the default ggplot theme
    fitfit <- tibble(outcome=eeg_measures[eeg_inds_plot]) %>%
      rowwise() %>%
      mutate(
          mod = 
            lmer(str_glue(paste("{outcome} ~ 1 + ",kin_measures[mi]," + group_char + ",kin_measures[mi],":group_char + (1|subj_char)")), data=tmpt)%>%
            list()
      )
    for(modi in 1:length(eeg_measures[eeg_inds_plot])){
      eegi = eeg_inds_plot[modi]
      tmpt <- tmpt %>%
        mutate(fit.m = predict(fitfit$mod[[modi]], re.form = NA),
               fit.c = predict(fitfit$mod[[modi]], re.form = NULL))
      print(
        tmpt %>%
          ggplot(aes(x = .data[[kin_measures[mi]]], y = .data[[eeg_measures[eegi]]], group = subj_char, col=group_char)) +
          geom_point(pch=16, size=2, alpha=0.5) +
          geom_line(aes(x= .data[[kin_measures[mi]]], y=fit.c, group = subj_char),color="grey", size = .1) +
          geom_line(aes(x= .data[[kin_measures[mi]]], y=fit.m, col = group_char), size = 2)+
          facet_wrap(vars(group_char))+
          ggtitle(eeg_measures[eegi])+ 
          guides(group="none")
      )
    }
    
    # t_out <- as_kable_extra(tbl, format = "latex") %>%
    #   add_header_above(c("Changes in ",kin_measures[mi],"for Cluster: ",clusters[ci])) %>%
    #   kable_styling(latex_options="scale_down")
    # cat(knitr::knit_print(t_out));
    # if (mi%%2 == 0){
    #   cat('\\clearpage');
    # }
  }
}
```
## LME EEG ~ 1+kin+group
```{r eegkingroup, echo=FALSE, message=FALSE, results="asis"}
library(gtsummary)
for (ci in cluster_inds_plot) {
  tmpt <- filter_at(eegt,vars('cluster_id'), any_vars(. %in% clusters[ci]));
  for(ki in kin_inds_plot){
    tmpt = tmpt[complete.cases(tmpt[[kin_measures[ki]]]),]
  }
  for (mi in 1:length(kin_measures)) {
    tbl <- tibble(outcome=eeg_measures[eeg_inds_plot]) %>%
      rowwise() %>%
      mutate(
        tbl = 
          lmer(str_glue(paste("{outcome} ~ 1 + ",kin_measures[mi]," + group_char + (1|subj_char)")), data=tmpt) %>%
          tbl_regression(tidy_fun = broom.mixed::tidy,
                         pvalue_fun = purrr::partial(style_pvalue, digits = 2),
                         intercept=TRUE) %>%
          add_global_p() %>%
          add_q() %>%
          list()
        ) %>%
      pull(tbl) %>% 
      tbl_merge(tab_spanner=eeg_title_chars[eeg_inds_plot])
    
    t_out <- as_gt(tbl) %>%
      gt::tab_header(title=c("Changes in ",kin_measures[ki],"for Cluster: ",clusters[ci])) %>%
      gt::tab_options(table.layout = "fixed") %>%
      gt::as_raw_html()
    print(t_out)
    
    rsq <- tibble(outcome=eeg_measures[eeg_inds_plot]) %>%
    rowwise() %>%
    mutate(
        mod = 
          lmer(str_glue(paste("{outcome} ~ 1 + ",kin_measures[ki]," + group_char + (1|subj_char)")), data=tmpt) %>%
          r.squaredGLMM(),
          print(str_glue("{outcome}\n R2m: {round(mod[1],4)},\tR2c: {round(mod[2],4)}\n\n"))
    )
    
    #%% VISUALIZATION OF MODELS
    theme_set(theme_classic()) # This sets the default ggplot theme
    fitfit <- tibble(outcome=eeg_measures[eeg_inds_plot]) %>%
      rowwise() %>%
      mutate(
          mod = 
            lmer(str_glue(paste("{outcome} ~ 1 + ",kin_measures[mi]," + group_char + (1|subj_char)")), data=tmpt) %>%
            list()
      )
    for(modi in 1:length(eeg_measures[eeg_inds_plot])){
      eegi = eeg_inds_plot[modi]
      tmpt <- tmpt %>%
        mutate(fit.m = predict(fitfit$mod[[modi]], re.form = NA),
               fit.c = predict(fitfit$mod[[modi]], re.form = NULL))
      print(
        tmpt %>%
          ggplot(aes(x = .data[[kin_measures[mi]]], y = .data[[eeg_measures[eegi]]], group = subj_char, col=group_char)) +
          geom_point(pch=16, size=2, alpha=0.5) +
          geom_line(aes(x= .data[[kin_measures[mi]]], y=fit.c, group = subj_char),color="grey", size = .1) +
          geom_line(aes(x= .data[[kin_measures[mi]]], y=fit.m, col = group_char), size = 2)+
          facet_wrap(vars(group_char))+
          ggtitle(eeg_measures[eegi])+ 
          guides(group="none")
      )
    }
      
    # t_out <- as_kable_extra(tbl, format = "latex") %>%
    #   add_header_above(c("Changes in ",kin_measures[mi],"for Cluster: ",clusters[ci])) %>%
    #   kable_styling(latex_options="scale_down")
    # cat(knitr::knit_print(t_out));
    # if (mi%%2 == 0){
    #   cat('\\clearpage');
    # }
  }
}
```
## LME EEG ~ 1+kin+group+speed+kin:group
```{r eegkingroupinterspeed, echo=FALSE, message=FALSE, results="asis"}
library(gtsummary)
for (ci in cluster_inds_plot) {
  tmpt <- filter_at(eegt,vars('cluster_id'), any_vars(. %in% clusters[ci]));
  for(ki in kin_inds_plot){
    tmpt = tmpt[complete.cases(tmpt[[kin_measures[ki]]]),]
  }
  for (mi in 1:length(kin_measures)) {
    tbl <- tibble(outcome=eeg_measures[eeg_inds_plot]) %>%
      rowwise() %>%
      mutate(
        tbl = 
          lmer(str_glue(paste("{outcome} ~ 1 + ",kin_measures[mi]," + group_char + ",kin_measures[mi],":group_char + (1|subj_char)")), data=tmpt) %>%
          tbl_regression(tidy_fun = broom.mixed::tidy,
                         pvalue_fun = purrr::partial(style_pvalue, digits = 2),
                         intercept=TRUE) %>%
          add_global_p() %>%
          add_q() %>%
          list()
        ) %>%
      pull(tbl) %>% 
      tbl_merge(tab_spanner=eeg_title_chars[eeg_inds_plot])
    
    t_out <- as_gt(tbl) %>%
      gt::tab_header(title=c("Changes in ",kin_measures[ki],"for Cluster: ",clusters[ci])) %>%
      gt::tab_options(table.layout = "fixed") %>%
      gt::as_raw_html()
    print(t_out)
    
    rsq <- tibble(outcome=eeg_measures[eeg_inds_plot]) %>%
    rowwise() %>%
    mutate(
        mod = 
          lmer(str_glue(paste("{outcome} ~ 1 + ",kin_measures[mi]," + group_char + ",kin_measures[mi],":group_char + (1|subj_char)")), data=tmpt) %>%
          r.squaredGLMM(),
          print(str_glue("{outcome}\n R2m: {round(mod[1],4)},\tR2c: {round(mod[2],4)}\n\n"))
    )
    
    #%% VISUALIZATION OF MODELS
    theme_set(theme_classic()) # This sets the default ggplot theme
    fitfit <- tibble(outcome=eeg_measures[eeg_inds_plot]) %>%
      rowwise() %>%
      mutate(
          mod = 
            lmer(str_glue(paste("{outcome} ~ 1 + ",kin_measures[mi]," + group_char + ",kin_measures[mi],":group_char + (1|subj_char)")), data=tmpt)%>%
            list()
      )
    for(modi in 1:length(eeg_measures[eeg_inds_plot])){
      eegi = eeg_inds_plot[modi]
      tmpt <- tmpt %>%
        mutate(fit.m = predict(fitfit$mod[[modi]], re.form = NA),
               fit.c = predict(fitfit$mod[[modi]], re.form = NULL))
      print(
        tmpt %>%
          ggplot(aes(x = .data[[kin_measures[mi]]], y = .data[[eeg_measures[eegi]]], group = subj_char, col=group_char)) +
          geom_point(pch=16, size=2, alpha=0.5) +
          geom_line(aes(x= .data[[kin_measures[mi]]], y=fit.c, group = subj_char),color="grey", size = .1) +
          geom_line(aes(x= .data[[kin_measures[mi]]], y=fit.m, col = group_char), size = 2)+
          facet_wrap(vars(group_char))+
          ggtitle(eeg_measures[eegi])+ 
          guides(group="none")
      )
    }
    
    # t_out <- as_kable_extra(tbl, format = "latex") %>%
    #   add_header_above(c("Changes in ",kin_measures[mi],"for Cluster: ",clusters[ci])) %>%
    #   kable_styling(latex_options="scale_down")
    # cat(knitr::knit_print(t_out));
    # if (mi%%2 == 0){
    #   cat('\\clearpage');
    # }
  }
}
```
## LME EEG ~ 1+kin+group+speed
```{r eegkingroupspeed, echo=FALSE, message=FALSE, results="asis"}
library(gtsummary)
for (ci in cluster_inds_plot) {
  tmpt <- filter_at(eegt,vars('cluster_id'), any_vars(. %in% clusters[ci]));
  for(ki in kin_inds_plot){
    tmpt = tmpt[complete.cases(tmpt[[kin_measures[ki]]]),]
  }
  for (mi in 1:length(kin_measures)) {
    tbl <- tibble(outcome=eeg_measures[eeg_inds_plot]) %>%
      rowwise() %>%
      mutate(
        tbl = 
          lmer(str_glue(paste("{outcome} ~ 1 + cond_char + ",kin_measures[mi]," + group_char + (1|subj_char)")), data=tmpt) %>%
          tbl_regression(tidy_fun = broom.mixed::tidy,
                         pvalue_fun = purrr::partial(style_pvalue, digits = 2),
                         intercept=TRUE) %>%
          add_global_p() %>%
          add_q() %>%
          list()
        ) %>%
      pull(tbl) %>% 
      tbl_merge(tab_spanner=eeg_title_chars[eeg_inds_plot])
    
    t_out <- as_gt(tbl) %>%
      gt::tab_header(title=c("Changes in ",kin_measures[ki],"for Cluster: ",clusters[ci])) %>%
      gt::tab_options(table.layout = "fixed") %>%
      gt::as_raw_html()
    print(t_out)
    
    rsq <- tibble(outcome=eeg_measures[eeg_inds_plot]) %>%
    rowwise() %>%
    mutate(
        mod = 
          lmer(str_glue(paste("{outcome} ~ 1 + cond_char +",kin_measures[ki]," + group_char + (1|subj_char)")), data=tmpt) %>%
          r.squaredGLMM(),
          print(str_glue("{outcome}\n R2m: {round(mod[1],4)},\tR2c: {round(mod[2],4)}\n\n"))
    )
    
    #%% VISUALIZATION OF MODELS
    theme_set(theme_classic()) # This sets the default ggplot theme
    fitfit <- tibble(outcome=eeg_measures[eeg_inds_plot]) %>%
      rowwise() %>%
      mutate(
          mod = 
            lmer(str_glue(paste("{outcome} ~ 1 + cond_char +",kin_measures[mi]," + group_char + (1|subj_char)")), data=tmpt) %>%
            list()
      )
    for(modi in 1:length(eeg_measures[eeg_inds_plot])){
      eegi = eeg_inds_plot[modi]
      tmpt <- tmpt %>%
        mutate(fit.m = predict(fitfit$mod[[modi]], re.form = NA),
               fit.c = predict(fitfit$mod[[modi]], re.form = NULL))
      print(
        tmpt %>%
          ggplot(aes(x = .data[[kin_measures[mi]]], y = .data[[eeg_measures[eegi]]], group = subj_char, col=group_char)) +
          geom_point(pch=16, size=2, alpha=0.5) +
          geom_line(aes(x= .data[[kin_measures[mi]]], y=fit.c, group = subj_char),color="grey", size = .1) +
          geom_line(aes(x= .data[[kin_measures[mi]]], y=fit.m, col = group_char), size = 2)+
          facet_wrap(vars(group_char))+
          ggtitle(eeg_measures[eegi])+ 
          guides(group="none")
      )
    }
      
    # t_out <- as_kable_extra(tbl, format = "latex") %>%
    #   add_header_above(c("Changes in ",kin_measures[mi],"for Cluster: ",clusters[ci])) %>%
    #   kable_styling(latex_options="scale_down")
    # cat(knitr::knit_print(t_out));
    # if (mi%%2 == 0){
    #   cat('\\clearpage');
    # }
  }
}
```